%-------------------------
% Resume in Latex
% Template by Sourabh Bajaj (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Swanand Mathekar} & Email: \href{mailto:swanandmathekar@gmail.com}{swanandmathekar@gmail.com} \\
  \href{https://swanand01.github.io/}{swanand01.github.io} $|$ \href{https://www.linkedin.com/in/swanand-mathekar/}{linkedin.com/in/swanand-mathekar} & Mobile: +91-930-787-3011 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {rtCamp}{Remote}
      {Senior Software Engineer}{Jul 2023 -- Present}
      \resumeItemListStart
        \item\small{Contributed to \textbf{Google WebStories} (WordPress.org plugin, 200k+ installs) — introduced the audio sticker element and implemented editor pre-rendering, eliminating load-time lag entirely.\vspace{-2pt}}
        \item\small{Shipped production features for \textbf{Google Chrome PSAT} — improved third-party cookie detection accuracy in the CLI and built key panels for the Chrome DevTools extension.\vspace{-2pt}}
        \item\small{Co-developed \textbf{SnapWP}, an open-source headless WordPress framework; designed the package architecture and built the Next.js integration layer.\vspace{-2pt}}
        \item\small{Built and maintained full-stack WordPress solutions for enterprise clients — custom PHP plugins, Gutenberg block themes, and REST/GraphQL API extensions.\vspace{-2pt}}
        \item\small{Implemented LLM-powered site-wide vector search integrated into WordPress themes, cutting manual content discovery overhead for clients.\vspace{-2pt}}
        \item\small{Authored comprehensive Puppeteer end-to-end test suites; delivered SEO-optimised, Core Web Vitals--compliant frontends.\vspace{-2pt}}
      \resumeItemListEnd

    \resumeSubheading
      {Lana Health}{Remote}
      {SDE Intern}{Jul 2022 -- Jun 2023}
      \resumeItemListStart
        \item\small{Built the full patient management dashboard in React — covering patient onboarding, in-admission education assignment, medication assignment, and medication tracking.\vspace{-2pt}}
        \item\small{Designed and implemented the analytics section with custom graphing components to surface patient and usage metrics for clinical staff.\vspace{-2pt}}
        \item\small{Built backend APIs using Dropwizard and Java to interface with FHIR-compliant health data systems.\vspace{-2pt}}
      \resumeItemListEnd

    \resumeSubheading
      {Enalo}{Remote}
      {SDE Intern}{Feb 2022 -- Apr 2022}
      \resumeItemListStart
        \item\small{Optimised existing transaction APIs by up to 30\% and reduced PostgreSQL query time.\vspace{-2pt}}
        \item\small{Implemented business banking interface applications using Python.\vspace{-2pt}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://pune.pinzo.app/}{Pinzo}}
      {Crowdsourced rent transparency platform for Pune. Built on Cloudflare Workers + D1 + Hono with a React frontend; reached 300+ anonymous pins in the first week. Implemented AI-powered flatmate matching using vector embeddings.}
    \resumeSubItem{autoMCC}
      {Autonomous AI agent to classify a company's Merchant Category Code from its website. Built a LangGraph reasoning agent with browser automation to crawl, extract, and map business content to regulated MCC codes.}
    \resumeSubItem{\href{https://collabcode.app/}{CollabCode}}
      {Open-source collaborative coding environment with a real-time shared editor, in-browser code execution, collaborative whiteboard, and voice/video. Built with React, Yjs, and Hocuspocus}
    \resumeSubItem{\href{https://pulse-m9g2.onrender.com/}{Pulse}}
      {Open-source P2P file sharing web app built with NodeJS, ExpressJS, SocketIO, and the WebTorrent protocol for fast cross-device transfers.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Savitribai Phule Pune University}{Pune, India}
      {B.E., Information Technology;  GPA: 9.2/10.0}{2019 -- 2023}
  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item\small{\textbf{Languages}{: Python, PHP, Java, JavaScript (ES6), TypeScript, SQL} \hfill \textbf{Platforms}{: Cloudflare Workers, AWS, Azure}}\vspace{-4pt}
   \item\small{\textbf{Frameworks}{: React, Node.js, WordPress, Django, Flask, Hono} \hfill \textbf{Tools}{: Git, Docker, PostgreSQL, LangGraph}}
 \resumeSubHeadingListEnd


%--------CERTIFICATES------------
\section{Certificates}
 \resumeSubHeadingListStart
   \item\small{
     \href{https://www.kaggle.com/learn/certification/swanandmathekar/python}{Python} \textbar{}
     \href{https://www.kaggle.com/learn/certification/swanandmathekar/intro-to-machine-learning}{Machine Learning} \textbar{}
     \href{https://learn.microsoft.com/api/credentials/share/en-us/SwanandM-7652/344706EC24B39F76?sharingId=D4DB318B4BD86C22}{Azure Fundamentals (AZ-900)}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
